A Data-Driven Framework for Neural Field Modeling

### 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex
added few words and references for online algorithm

\mike{A further extension of the framework is to allow for the algorithm to learn online. The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected. A simple real-time implementation can be achieved using the UKF  and an online recursive  LS estimator \cite{Ljung1999}, more sophisticated approaches include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.}

>>>>

\mike{A further extension of the framework is to allow for the algorithm to learn online. The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected. \parham{A simple real-time implementation can be achieved using the UKF  and an online recursive  LS estimator \cite{Ljung1999}, more sophisticated approaches include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.}}
